---
title: "Supervision Setup"
output:
  xaringan::moon_reader:
    css: ["xaringan-themer.css", "ppt_style.css"]
    lib_dir: libs
    nature:
      highlightStyle: monokai
      highlightLines: true
      highlightSpans: true
      ratio: '16:9'
---


```{r setup, include=FALSE}
library(xaringanthemer)
library(xaringanExtra)
library(tidyverse)
library(broom)
library(papaja)
library(ggcats)
library(ggimage)


options(htmltools.dir.version = FALSE)

```

```{r xaringan-themer, include=FALSE, warning=FALSE}

style_mono_light(base_color = "#23395b")
```

class: center, middle

# Intros & [Webpage](https://desupervision.netlify.app/)


---

# Projects

- Option 1:  The effectiveness of game-fiction/gamification for learning R/stats, measured by cognitive/motivational outcomes with [Dr Milan Valášek](https://and.netlify.app/docs/escape/)

<br>

- Option 2: A survey/online study around maths with Prof Andy Field

<br>

- Option 3: *Other* (but you'll be less supported...)

---

class: center, middle

# Groundwork Form


---

# R Project Setup


- Download [`papaja`](https://desupervision.netlify.app/rmarkdown_tutorial.html)


- Create dissertation RProject


- Open a new Rmd file from papaja template 


- Create .bib file











